High-Dimensional Regularized Discriminant Analysis

### 2016-01-20 reports/paper-hdrda.Rnw
Applied a couple of edits from Caleb.

The \emph{HDRDA} implementation of \eqref{eq:hdrda-decomposed} in the {\tt
  sparsediscrim} R package was comparable to that of the diagonal classifiers in
terms of computational runtime. Given the \emph{RDA} classifier from
\cite{Friedman:1989tm} has been shown to have excellent performance in the
high-dimensional setting \citep{Webb:2011vu} but is limited by its
computationally intense model selection procedure, our work enables the
\emph{RDA} classifier to be employed with small-sample, high-dimensional data in
practice. This results is reassuring because the \emph{RDA} classifier remains
widely popular in the literature. In fact, variants of the RDA classifier have
been applied to microarray data
\citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te}, facial recognition
\citep{Ching:2012fu,Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we},
handwritten digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep*{Wu:1996us,Aeberhard:1993fp}.

The dimension reduction that we have employed in this paper has reduced the
dimension to rank$(\widehat{\bm \Sigma}) = q$. An interesting extension of
our work would reduce the dimension $q$ further to a lower dimension $q_L < q$
using some criterion proposed, perhaps similar to that employed in principal
components analysis. While it is not clear whether classification performance
would improve via such a method, the efficiency of the training and model
selection would certainly improve. Moreover, if $q_L = 2$ or $3$ was selected,
the potential for low-dimensional graphical displays of high-dimensional could
be accomplished.

>>>>

The \emph{HDRDA} implementation of \eqref{eq:hdrda-decomposed} in the {\tt
  sparsediscrim} R package was comparable to that of the diagonal classifiers in
terms of computational runtime. Given the \emph{RDA} classifier from
\cite{Friedman:1989tm} has been shown to have excellent performance in the
high-dimensional setting \citep{Webb:2011vu} but is limited by its
computationally intense model selection procedure, our work enables the
\emph{RDA} classifier to be employed with small-sample, high-dimensional data in
practice. This result is reassuring because the \emph{RDA} classifier remains
widely popular in the literature. In fact, variants of the RDA classifier have
been applied to microarray data
\citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te}, facial recognition
\citep{Ching:2012fu,Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we},
handwritten digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep*{Wu:1996us,Aeberhard:1993fp}.

The dimension reduction that we have employed in this paper has reduced the
dimension to rank$(\widehat{\bm \Sigma}) = q$. An interesting extension of our
work would reduce the dimension $q$ further to a lower dimension $q_L < q$ using
some criterion proposed, perhaps similar to that employed in principal
components analysis. While it is not clear whether classification performance
would improve via such a method, the efficiency of the training and model
selection would certainly improve. Moreover, if $q_L = 2$ or $3$ was selected,
the potential for low-dimensional graphical displays of high-dimensional data
could be accomplished.
